Preliminary categorisation of SpaceWarps candidates

### 2016-04-13 paper2.tex
compiling without error

@@

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}
%\usepackage{ae,aecompl}

@@

% Only include extra packages if you really need them. Common packages are:
\usepackage[dvipdfmx]{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
%\usepackage{bmpsize}

@@

\newcommand{\inclfig}[2]{
  \centering
  \includegraphics[width=0.49\linewidth]{spaghetti/#2_input} %
  \includegraphics[width=0.49\linewidth]{spaghetti/#2_img1} \\
  \includegraphics[width=0.49\linewidth]{spaghetti/#2_img3_ipol} %
  \includegraphics[width=0.49\linewidth]{spaghetti/#2_img2} \\
  \includegraphics[width=1\linewidth]{masses/#1_#2_mstel_vs_mtot}
}

\newcommand{\lenstitle}[1]{\noindent\textit{#1} --}

@@

%TODO append this to the bibliography file (bibli.bib)
% References
% Keeton C.
% R., 2002, “A Catalog of Mass Models for Gravitational Lensing”, arXiv:astro-ph/0102341v2

@@

\subsection{plausible}

@@

>>>>

\usepackage{silence} % silence error warinings
\WarningFilter{caption}{Unsupported document class} % caption doesn't know mnras..

@@

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc} % make sure font is supported
% \usepackage{ae,aecompl} %obsolete when using modern fonts
\usepackage[final]{microtype} % make sure font is supported
% and a suitable font
\usepackage{lmodern} % use a modern font with T1 support
%\usepackage{cm-super} % use a modern font with T1 support

@@

% Only include extra packages if you really need them. Common packages are:
%\usepackage[dvipdfmx]{graphicx}	% Including figure files
\usepackage{graphicx} % Including figure files
\usepackage[skip=0pt]{subcaption}
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
%\usepackage{bmpsize}  % PS still needs this for correct bounding boxes?

% TODO stuff, comment out for final submit
\usepackage{todonotes} % as long as we are editing...
\usepackage{showframe} % for debug
\overfullrule=5pt      % show overfull boxes

@@

\newcommand{\inclfig}[2]{
  \centering
  \begin{subfigure}{0.5\linewidth}
    \includegraphics[width=\linewidth]{spaghetti/#2_input}
  \end{subfigure}%
  \begin{subfigure}{0.5\linewidth}
    \includegraphics[width=\linewidth]{spaghetti/#2_img1}
  \end{subfigure}%
  \\[-1px]%
  \begin{subfigure}{0.5\linewidth}
    \includegraphics[width=\linewidth]{spaghetti/#2_img3_ipol}
  \end{subfigure}%
  \begin{subfigure}{0.5\linewidth}
    \includegraphics[width=\linewidth]{spaghetti/#2_img2}
  \end{subfigure}%
  \\[-1px]%
  \begin{subfigure}[b]{\linewidth}
    \includegraphics[width=\linewidth]{masses/#1_#2_mstel_vs_mtot}
  \end{subfigure}
}

\newcommand{\lenstitle}[1]{\noindent\textbf{#1} --}

@@

@@

\subsection{plausible}
  The plausible candidates fail in one category, but are quite convincing in all the others.
  Thats why we recomend them for a following up study for ...

@@

\newpage

\section{TODO}
\listoftodos

\todo{REMOVE TODOS at the end}
